\documentclass[10pt]{report}
\usepackage{a4,fullpage}
 
%\advance\textwidth 1cm
%\advance\textheight 1cm
%\advance\oddsidemargin -1cm
%\advance\evensidemargin -1cm
%\advance\topmargin -1cm

\parindent=0pt

%\input{mgcv.sty}
\usepackage{mgcv}

\begin{document}
\pagestyle{headings}
\thispagestyle{empty}

\begin{flushleft}
\textbf{{\LARGE{}Kyle C. Gordon }}
\end{flushleft}

\hligne

%\begin{flushleft}
%This is a test line on the left \hfill This is a line on the right hand side
%\end{flushleft}
%\begin{flushright}
%This is right aligned instead.
%\end{flushright}

%\begin{flushright}
%Flat 2/2\\
%Rothesay Court\\
%2471 Dumbarton Road\\
%Glasgow\\
%G14 0NT\\
%{\it Tel:} 07979 825870\\
%{\it Email: }kyle@lodge.glasgownet.com\\
%\url{http://lodge.glasgownet.com}
%\end{flushright}

%\begin{flushleft}
%D.O.B. 7th October 1980
%Non-Smoker\\
%Full driving licence
%\end{flushleft}

\begin{flushleft}
D.O.B. 7th October 1980	\hfill 19 Cander Rigg\\
Full driving licence - no endorsements \hfill Bishopbriggs\\
Non-smoker\hfill Glasgow\\
\hfill G64 3LR\\
\hfill{\it Tel:} 07979 825870\\
\hfill{\it Email: }kyle@lodge.glasgownet.com\\
\hfill\url{http://lodge.glasgownet.com}
\end{flushleft}

%\begin{flushleft}
%\bf{\underline{School}}\\
%\end{flushleft}

%\begin{flushleft}
%The High School of Glasgow, Anniesland, Glasgow\\
%Attained 7 Standard Grades and 4 Highers
%\end{flushleft}

%\begin{flushleft}
%\bf{\underline{University}}\\
%\end{flushleft}

%\begin{flushleft}
%University of Paisley\\
%BSc Information Technology \\
%(Computer Networking)
%\end{flushleft}

\begin{flushleft}
\bf{\underline{Education}}\\
\end{flushleft}

\begin{flushleft}
University of Paisley - BSc Information Technology (Computer Networking)\\
The High School of Glasgow, Anniesland, Glasgow\\
\end{flushleft}

\begin{flushleft}
\bf{\underline{Personal Profile}}\\
\end{flushleft}

LPI, Novell, and MongoDB certified systems administrator with a wide range of Linux, Microsoft, and networking experience within the computer industry. Experienced in DevOps methodologies and systems, with first class analytical, design and problem solving skills, and a view to maintaining the highest service standards. Excellent verbal and written skills with the ability to work independently, or as part of a team. A wide range of skills, from supporting large IP networks, desktop and server applications, backup systems, to server operation and maintenance, compute cluster management, helpdesk management and platform build decision making.

\begin{flushleft}
\bf{\underline{Major Achievements}}\\
\end{flushleft}

\begin{itemize}
\item Led project to replace primary customer facing and backend infrastructure with Suse Linux Open Enterprise Server across entire organization.
\item Debian user and administrator for over 12 years, and Novell Suse Linux Enterprise 11 certified administrator.
\item Technical lead for all Linux services on 80+ servers within a national NHS board, and technical lead for migration to the national Alfresco electronic document management system hosted on Linux and Oracle.
\item Designed and project led the implementation of the DNS infrastructure within the organization of 800 users.
\item Part of a small target driven team to develop and deploy network infrastructure, VoIP communications, desktops and servers to a new 150+ seat office within 5 weeks.
\item Evangelised Open Source technologies and methods to the Network Services department, resulting in deployment, use and support in all offices across Scotland.
\item Introduced and championed pro-active systems administration and build automation, using Nagios, AutoYast, and Puppet, resulting in record availability and security.
\item Moved digital animation company of 50 employees to a new build location with no interruption to production.
\item Dealt with architects, project manager, electrical and building engineers to co-ordinate all matters relating to IT services regarding the new location prior to and during the build.
\item Migrated company from Windows 2000 and Exchange 2000 servers to Linux servers and utilizing Microsoft Active Directory for identity management.
\item Ensured continued growth of IT facilities whilst retaining backwards availability and continuation of service.
\item Successfully instigated rolling renderfarm cluster upgrades and redeployments to aid system availability and manageability, whilst under pressure to ensure existing projects were not impacted in a 24/7 organization.
\item Documented all aspects of IT functionality to assist management reach availability and manageability targets.
\item Developed and built LiveCD based distributed build cluster for aKademy 2007 KDE conference.
\end{itemize}

\clearpage 

\begin{flushleft}
\bf{\underline{Career History}}\\
\end{flushleft}

\begin{flushleft}
May 2013 - Present - Linux Systems Cloud Engineer\\
{\bf iBAHN, Global Operations}\\
iBAHN, Stirling\\
Linux Systems Cloud Engineer operating within a small core team of engineers developing and maintaining the next generation high speed internet access product and associated systems. Extensive use of Git, Bash, Puppet and Foreman to manage critical internal and customer facing systems on cloud infrastructure. Deployment of Jenkins and associated services to enable a continuous integration and deployment environment in a Ruby, C++ and C orientated DevOps driven workplace, along with automation of other regular tasks, and final tier support for IPTV and HSIA products.\\
\end{flushleft}

\begin{flushleft}
July 2006 - April 2013 - Network Administrator\\
{\bf NHS Education for Scotland}\\
National Health Service, Glasgow\\
Network and systems administrator with local responsibility for over 250+ users within three regional offices in Glasgow, and national responsibility for 80+ Linux servers around Scotland. Liaising closely with remote team members to ensure a consistent IT framework, I was technical lead for the national DNS \& DHCP system, Linux server management and maintenance, and the national Oracle/ECMS deployment. Core involvement with the deployment of desktop services, automated build and deployment services, production networks, virtualization and storage platforms, and Open Source software solutions. I rely heavily on cluster management methodologies to manage servers, desktops and laptops remotely, through the use of core DHCP, DNS \& TFTP tools through higher level management interfaces.\\
During the deployment of a regional office, I handled the configuration, installation and management of our integrated Cisco network and Avaya VoIP telephone network.\\ I was also responsible for a large portion of IT related purchasing and installation, dealing with multiple suppliers, contractors and service agreements.
\end{flushleft}

\begin{flushleft}
February 2004 - July 2006 - Systems Administrator\\
{\bf Absolute Studios Ltd}\\
Digital Media Center, Glasgow\\
Systems Administrator handling the management and maintenance of a 200 node Windows 2000 based HPC cluster, with dedicated network and storage systems, and evaluation and deployment of back end GNU/Linux Servers. Experience gained with Veritas BackupExec, Symantec AntiVirus, Microsoft Active Directory, Exchange, Software Management and Deployment, Dynamic DNS and DHCP, Software Update Services, Automated Deployment as well as desktop maintenance and support. Valuable experience gained in LDAP and Kerberos based authentication systems, and integration of Open Source software solutions into a Microsoft environment. \\
Delivered and operated the HPC cluster to serve the needs of the digital animation production house.\\
Tasks also involved the care and maintenance of a variety of artistic software packages, and qualified hardware, and the requisite tasks involved in the smooth running of the company renderfarm. Responsible for the IT department budget, recommendations and purchases of all aspects of the computing facilities and supplies. Moved IT infrastructure to new facilities, liaising with building contractors and consultants in order to provide the correct services. Ensured UPS availability, environmental monitoring, core network, intrusion detection systems and updated acceptable use policies were prepared and ready for first use.\\
\end{flushleft}


\begin{flushleft}
September 2003 - February 2004 - Advanced Unix Monitoring Specialist\\
{\bf Sun Microsystems}\\
Sun Microsystems, Linlithgow\\
Monitoring package specialist, part of a team of 8 providing round the clock support for the NetConnect, Configuration and Service Tracker, and Utility Computing packages to Sun Microsystems global client base. Expertise gained in Solaris 9 environment, and system administration of the test environment.\\
\end{flushleft}

\clearpage

\begin{flushleft}
January 2003 - September 2003 - Linux Support Analyst\\
{\bf XCalibre Communications Ltd}\\
Kirkton Campus, Livingston\\
Linux Support Analyst, part of a team of five responsible for the smooth running of the datacenter and server farm. Took part in physical movement of datacenter between hosting facilities over a three day period, without losing customer focus. Supported high availability systems, system integration and monitoring. Assisted maintenance of 20,000 zonefiles and associated replication system, multiple database systems and table replication, custom Apache configurations and Exim/MySQL integration.\\
%\end{flushleft}
%\begin{flushleft}
Projects included reconfiguration and redeployment of the Netsaint monitoring suite and upgrade to Nagios. Integration of the monitoring systems with trend analysis and alerting systems to ensure continuing customer focus.
\end{flushleft}


\begin{flushleft}
1999 - January 2003 - Systems Administrator\\
{\bf Consol Suncenters Ltd}\\
Maryhill, Glasgow\\
Part-time Systems Administrator whilst at university for the head office network. Experience gained in office life and computer networks in a client-server environment. Gained knowledge of Linux in a business critical environment, and client/server systems such as Samba (including domain controllers and roaming profiles), email transports, DHCP, DNS, security policies and firewalls. Responsible for the purchase and maintenance of new hardware and associated software, including an upgrade of the entire network from 10BaseT to 100BaseTX. Also responsible for maintenance of all ISDN equipment within the facility.
\end{flushleft}

%\begin{flushleft}
%August 1998 - January 2003 - Replenishment/Checkout Assistant\\
%{\bf J. Sainsbury PLC}\\
%Partick, Glasgow
%\end{flushleft}

%\begin{flushleft}
%\end{flushleft}

\begin{flushleft}
\bf{\underline{Interests}}
\end{flushleft}

\begin{flushleft}
\underline{Computing}
\end{flushleft}

\begin{flushleft}
I firmly believe in an integrated network, and as such all video, audio, storage and compute technologies around the home are orientated around a core Gigabit network, complemented by my active interest in electronics, DIY, and home automation.
I have used Debian since 1999, and therefore I have always ensured my skills are cross platform, and regularly code tools and scripts in both Python and Bash.
Early member, and operator, of the Scottish Linux User Group and \#scotlug
\end{flushleft}

\begin{flushleft}
\underline{Motorsport}
\end{flushleft}

\begin{flushleft}
I am a licensed by the Motor Sports Association as a National Race and Rally Timekeeper, and work in association with Scottish Motorsport Automatic Race Timing (SMART).
The SMART team provides timing services to fast paced race meetings and national rallies throughout the UK. I also provide independent timekeeping services to televised events, and enjoy the time critical nature of the events.
\end{flushleft}

\begin{flushleft}
\underline{Vehicles}
\end{flushleft}

\begin{flushleft}
I own and maintain three classic vehicles which I enjoy driving and taking to classic car events. I sit on the committee of the Scottish Western Thoroughbred Car Club, and often assist other clubs with their events when required.
\end{flushleft}

\begin{flushleft}
\bf{\underline{References}}
\end{flushleft}

\begin{flushleft}
Available on request
\end{flushleft}


%\par\nopagebreak\vfill\hfill \today
\par\nopagebreak\hfill \today

\end{document}
